# Data pre-processing

## Libraries

```{r}
#| eval: true
#| echo: true
#| warning: false
#| error: false
#| output: false
library(tidyverse)
library(stringr)
library(ggplot2)
```

The manually annotated data titled `data/WEIRD coding final corr names.csv` was cleaned through process captured in `weird data cleaning.R` script.

Here we take this manually annotated and cleaned data, `data/WEIRD part cleaned Feb24.csv`. 

```{r}
#| eval: true
#| echo: true
#| output: asis
d <- read.csv('data/WEIRD part cleaned Feb24.csv',header = TRUE)
knitr::kable(d[1:5,1:5])
```

## Preprocess

In the preprocessing, we add elements to the data (WEIRD and non-WEIRD country codes, paper, study, sample ids, expand samples, and various other operations).

This preprocessing creates four data frames used in subsequent analyses.

```{r}
#| eval: true
#| echo: true
source('scripts/preprocess.R')
```

### Description of data frames

* `d` is the original data with `r nrow(d)` observations. Each row refers to a study (not article).

* `D` is a version of the original data containing empirical/human studies with `r nrow(D)` observations. Each row refers to a study (not article).

* `df` contains samples within studies with `r nrow(df)` observations.

* `DF` contains samples with redundant samples removed. It has `r nrow(DF)` observations.

Within the data, there are `r sum(df$study_id=='study1' & df$sample_id=='sample0')` articles.

We have created a identifier for articles (`paper_id`), studies (`study_id`), and samples (`sample_id`) and a unique identifier which combines these (`paper_id_study_id`).

### Description of variables

* `CountryDataCollected_WEOG` is based on WEIRD country index derived from Krys et al., (2014).
* `FirstAuthorCountry_WEOG` is based on WEIRD country index derived from Krys et al., (2014).
* `gender_balance` is the proportion of females in the samples
* ... (to be continued)


```{r}
#| eval: true
#| echo: true
names(d)

```

Save (if necessary)

```{r}
#| output: asis
needs_saving <- FALSE
if(needs_saving==TRUE){
  save(d,df,D,DF,file='data/WEIRD_data.Rdata')
}
```
