# Data pre-processing

## Libraries

```{r}
#| eval: true
#| echo: true
#| warning: false
#| error: false
#| output: false
library(tidyverse)
library(stringr)
library(ggplot2)
```

The manually annotated data titled `data/WEIRD coding final corr names.csv` was cleaned through process captured in `weird data cleaning.R` script.

Here we take this manually annotated and cleaned data, `data/WEIRD_06_05_2024.csv`. 

```{r}
#| eval: true
#| echo: true
#| output: asis
d <- read.csv('data/WEIRD_06_05_2024.csv',header = TRUE)
knitr::kable(d[1:5,1:5])
```

## Preprocess

In the preprocessing, we add elements to the data (WEIRD and non-WEIRD country codes, paper, study, sample ids, expand samples, and various other operations).

This preprocessing creates four data frames used in subsequent analyses.

```{r}
#| eval: true
#| echo: true
source('scripts/preprocess.R')
```

### Description of data frames

* `d` is the original data with `r nrow(d)` observations. Each row refers to a study (not article).

* `D` is a version of the original data containing empirical/human studies with `r nrow(D)` observations. Each row refers to a study (not article).

* `df` contains samples within studies with `r nrow(df)` observations.

* `DF` contains samples with redundant samples removed. It has `r nrow(DF)` observations.

Within the data, there are `r sum(df$study_id=='study1' & df$sample_id=='sample0')` articles.

We have created a identifier for articles (`paper_id`), studies (`study_id`), and samples (`sample_id`) and a unique identifier which combines these (`paper_id_study_id`).

### Description of variables

* `CountryDataCollected_WEOG` is based on WEIRD country index derived from Krys et al., (2014).
* `FirstAuthorCountry_WEOG` is based on WEIRD country index derived from Krys et al., (2014).
* `gender_balance` is the proportion of females in the samples
* ... (to be continued)

* `PaperTitle`: enter the exact title of the article 
* `Year`: year published 
* `Journal`: journal published in 
* `FirstAuthorName`: enter the first author’s name in this format: Jakubowski, Kelly 
* `FirstAuthorCountry`: enter the country of the institution where the first author works 
 
* `CountryDataCollected`: enter the country(s) where the data was collected. If more than one country (e.g., for a cross-cultural study), please enter ALL countries where data was collected, separated by semi-colons, for example: UK; Mali; Uruguay 
OR online = for online studies with no origin country data collected 
 
* `SamplePrimaryCountryofOrigin`: enter the country where the majority of the sample came from (for instance, if 54% of the participants were from the UK, enter UK). If sample came equally from multiple countries (e.g. 1/3 of participants came from each of 3 countries), OR if the researchers explicitly recruited from different countries for the sake of making cross-national comparisons, then enter all countries separated by semi-colons, for example: UK; Mali; Uruguay  
* `Ethnicity`: if described, enter the ethnicity of the majority of the sample (e.g. if more than 50% were white, enter white). If split equally across ethnicities, you can enter more than one ethnicity, separated by semi-colons. Categories to be used here: Asian, black, white, Hispanic, other 
* `SampleSize`: enter total sample size as a number 
* `SampleAgeMean`: enter mean age of the sample 
* `SampleAgeSD`: enter the standard deviation of the age of the sample 
* `SampleOtherDescription`: if other description of sample such as ‘university students’ or ‘undergraduate students’ is provided, please add this here. Please try and retain consistent category labels across studies 
 
* `SampleMusicianshipDescription`: if the sample is described by the authors as only consisting of musicians, write ‘musicians’; if described as only non-musicians, write ‘non-musicians’; if sample included both, include both labels separated by a semi-colon (musicians; non-musicians) 
  
* `SamplingMethodDescription`: indicate category from the following list: volunteers, course credit, paid, other (if more than one of these categories is relevant, enter both, separated by a semi-colon such as: volunteers; paid) 
* `FemaleParticipantsNumber`: total number of female participants in the study 
* `MaleParticipantsNumber`: total number of male participants in the study   
* `MeanYearsEducation`: mean years of education of the sample 
* `MusicPrimaryGenre`: please enter the main/primary genre of music studied (if any) such as classical, pop, jazz, etc. If a study sampled equally across multiple genres, please enter these separated by semi-colons, for instance: classical; rock; punk. artificial = for artificial stimuli (beeps, clicks, sine waves, single sounds) 
* `MusicOriginCountry`: If a study used standard excerpts from styles such as classical, pop, rock, or jazz, please write Western, as it is likely such music came from US/UK/Western Europe primarily. For other, more international styles, please specify country from which the music comes (e.g., China, India).  
If a study utilised music from multiple origin counties, please enter these separated by semi-colons, for instance: Western; Mali; Uruguay 
  
* `MusicSource`: indicate category from the following list: precomposed, semi-precomposed, experimenter-created, other (note: ‘precomposed’ refers to music that was not composed specifically for the study, e.g. a Beethoven symphony or a commercially released pop song; ‘semi-precomposed’ refers to precomposed music that has been manipulated by the experimenter- for instance, a Beethoven symphony was converted to a single-line MIDI melody for the experiment) 
  
* `Comments`: you may use this column to optionally enter any problems/issues that you would like a second coder to check over; if none, then please just leave blank! 
  
* `CoderName`: enter your name 
  
* `Keywords`: enter all keywords as listed at the start of the article, separated by semi-colons, for instance: functional harmony; extended tonality; harmonic substitutions; music perception; musical syntax 


Save (if necessary)

```{r}
#| output: asis
needs_saving <- FALSE
if(needs_saving==TRUE){
  save(d,df,D,DF,file='data/WEIRD_data.Rdata')
}
```
