# Data pre-processing

## Libraries

```{r}
#| eval: true
#| echo: true
#| warnings: false
#| messages: false
library(tidyverse)
library(stringr)
library(ggplot2)
```

Take the manually annotated data.

```{r}
#| eval: true
#| echo: true
#| output: asis

rm(list=ls())
d <- read.csv('data/WEIRD part cleaned Feb24.csv',header = TRUE)
knitr::kable(d[1:5,1:5])
```

## Preprocess

Add and alter variables in the data.

```{r}
#| eval: true
#| echo: true

source('scripts/preprocess.R') # Preprocess data (includes WEIRD country index)
```

### Description of data frames

* `d` is the original data with `r nrow(d)` observations. Each row refers to a study (not article).

* `D` is a version of the original data containing empirical/human studies with `r nrow(D)` observations. Each row refers to a study (not article).

* `df` contains samples within studies with `r nrow(df)` observations.

* `DF` contains samples with redundant samples removed. It has `r nrow(DF)` observations.

Within the data, there are `r sum(df$study_id=='study1' & df$sample_id=='sample0')` articles.

We have created a identifier for articles (`paper_id`), studies (`study_id`), and samples (`sample_id`) and a unique identifier which combines these (`paper_id_study_id`)

### Description of variables

* `CountryDataCollected_WEOG` is based on WEIRD country index derived from Krys et al., (2014).
* `FirstAuthorCountry_WEOG` is based on WEIRD country index derived from Krys et al., (2014).
* `gender_balance` is the proportion of females in the samples


```{r}
#| eval: true
#| echo: true
names(d)

```

## Save (if necessary)

```{r}
#| output: asis
needs_saving <- FALSE
if(needs_saving==TRUE){
  save(d,df,D,DF,file='data/WEIRD_data.Rdata')
}
```
